Foreground Detection via Deep Variation Transformation

### 2018-12-16 draft.tex
Please enter the commit message for your changes. Lines starting  with '#' will be ignored, and an empty message aborts the commit.  On branch master  Changes to be committed: 	modified:   draft.aux 	modified:   draft.log 	modified:   draft.out 	modified:   draft.pdf 	modified:   draft.tex

@@

The network used in this work is devised as an end-to-end architecture,

@@

\subsection{Foreground Detection}
%As shown in the \reffig{flow_chart}, 
Then, the prediction maps can be reconstructed from the prediction patches.
%
Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
%
The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases},
\end{equation}

\begin{equation}
    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
\end{equation}
where the $M$ denotes the final foreground map given by our DPVTL model.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.

@@

The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.

>>>>

    \label{eq_reshape}

@@

% 描述网络结构
The network used in this work is devised as an end-to-end architecture XXX
The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
\todo{please improve the English of this paragraph}

@@

\subsection{Foreground Detection}
%As shown in the \reffig{flow_chart}, 
After the transformation of observations of pixels,
pixel patches feed into the network are transformed into the probability patches,
which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground for final results.
%
The comparison with threshold is mathematically shown as follows:
\begin{equation}
    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
\end{equation}
where XXX

Then the reverse procedure of \refeq{eq_reshape}

used to reconstruct the foreground image for the final results.
%

The network devised in proposed approach

Then, the prediction maps can be reconstructed from the prediction patches.
%
Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
%
The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases},
\end{equation}

where the $M$ denotes the final foreground map given by our DPVTL model.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.

@@
